Hypertension and microbiome

### 2019-03-22 articletwo.Rmd
Lacto coefficient to show

dir.create("rds/", showWarnings = FALSE)
```

@@

maaslin$lacto.max  <- maaslinwrapper(pseq = pseq.species.lactobacillus.core,
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced =c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03",
                          "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                taxa = paste0(lactotaxa, collapse = ","))
```

@@

```{r Reading maaslin lacto min output}
maas.lacto.results.df.signf <- maaslin$lacto.min %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="Variable", by.y = "Covariate") %>%
    dplyr::mutate(Qval = p.adjust(P.value, method="BH"),
                  beta = Coefficient) #%>%

maas.lacto.results.df.signf %>%
    select(Variable, Feature, P.value, Q.value) %>%
    arrange(Q.value) %>%
    kable
```

@@

```{r Reading maaslin lacto max output}
maas.lacto.results.df.signf <- maaslin$lacto.max %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="Variable", by.y = "Covariate") %>%
    dplyr::mutate(Qval = p.adjust(P.value, method="BH"),
                  beta = Coefficient) #%>%

>>>>

dir.create("rds/", showWarnings = FALSE)
dir.create("session/", showWarnings = FALSE)
```

@@

maaslin$lacto.max  <- maaslinwrapper(pseq = pseq.species.lactobacillus.core,
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced =c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03",
                          "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                taxa = paste0(lactotaxa, collapse = ","))

@@

```{r Reading maaslin lacto min output}
maaslin$lacto.min %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="Variable", by.y = "Covariate") %>%
    dplyr::mutate(Qval = p.adjust(P.value, method="BH"),
                  beta = Coefficient) %>% 
    select(Variable, Feature, Coefficient, P.value, Q.value) %>%
    arrange(Q.value) %>%
    mutate_if(is.numeric, funs(ifelse(. < 0.01, sprintf("%.1e", .), round(., 2)))) %>%
    kable
```

@@

```{r Reading maaslin lacto max output}
maaslin$lacto.max %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="Variable", by.y = "Covariate") %>%
    dplyr::mutate(Qval = p.adjust(P.value, method="BH"),
                  beta = Coefficient) %>%
    select(Variable, Feature, Coefficient, P.value, Q.value) %>%
    arrange(Q.value) %>%
    mutate_if(is.numeric, funs(ifelse(. < 0.01, sprintf("%.1e", .), round(., 2)))) %>%
    kable
```
